\huge Open, privacy-preserving protocols for lawful surveillance

### 2016-02-29 paper/intro.tex
Intro edits

\section{Introduction}\label{sec-introduction}
As networked devices become more available, more capable, and more ubiquitous
in everyday life, tension mounts between users' desire to safeguard their 
personal information and government agencies' desire to use that personal 
information in their pursuit of criminals and terrorists.  For example, 
both the heated (and still unresolved) discussion about the Snowden 
revelations that started in 2013 and the ongoing dispute between Apple and 
the US Justice Department are understood by many people
as examples of an unpleasant, stark choice: Citizens can either have
secure devices and control over their personal information, or they can have
law-enforcement and intelligence agencies with the tools that they need to
keep the country safe. We regard this stark choice as a false dichotomy and 
assert that, by deploying appropriate security technology in the context of 
sound policy and the rule of law, we can have both user privacy and effective 
law enforcement and intelligence.

Adopting the approach taken by Bandits~\cite{sff-foci2014}\footnote{For the
purpose of anonymization, we present an anonymized version of this manuscript and
refer to the authors throughout as ``Bandits''.}, we
seek to design and implement protocols for {\it accountable surveillance}.
We require that government surveillance be conducted according to {\it open
processes}, as defined in Section~\ref{sec-open} below, and that the privacy
of {\it untargeted users} be protected.  We consider the surveillance goals
of {\it set intersection} and {\it contact chaining} and show that both can 
be achieved in a privacy-preserving, accountable fashion.

>>>>

\section{Introduction}\label{sec-introduction}
As networked devices become more available, more capable, and more ubiquitous
in everyday life, tension mounts between users' desire to safeguard their 
personal information and government agencies' desire to use that personal 
information in their pursuit of criminals and terrorists.  For example, 
the heated (and still unresolved) discussion about the Snowden 
revelations that started in 2013 is understood by many people
as an example of an unpleasant, stark choice: Citizens can either have
control over their personal information, or they can have
law-enforcement and intelligence agencies with the tools that they need to
keep the country safe. We regard this stark choice as a false dichotomy and 
assert that, by deploying appropriate security technology in the context of 
sound policy and the rule of law, we can have both user privacy and effective 
law enforcement and intelligence.

We draw a distinction between law enforcment access to
third-party records held by businesses such as telephone companies,
and encrypted information stored on an individual's personal devices:
our work focuses on the former, not the latter.
In particular, we believe that lawful searches of third-party records
can be made much more security- and privacy-preserving than they currently are
without compromising law enforcement search capabilities.
We are {\em not} suggesting support for ``key escrowed'' encryption
or general backdoors in personal devices,
as is the topic of the ongoing conflict between the FBI and Apple.

Adopting the approach to third-party records search
taken by Bandits~\cite{sff-foci2014}\footnote{For the
purpose of anonymization, we present an anonymized version of this manuscript and
refer to the authors throughout as ``Bandits''.}, we
seek to design and implement protocols for {\it accountable surveillance}.
We require that government surveillance be conducted according to {\it open
processes}, as defined in Section~\ref{sec-open} below, and that the privacy
of {\it untargeted users} be protected.  We consider the surveillance goals
of {\it set intersection} and {\it contact chaining} and show that both can 
be achieved in a privacy-preserving, accountable fashion.
